\sysfull

### 2017-07-31 paper/background.tex

\subsection{Task-based Intermittent Computing}
\TODO{This sequential / modular split seems pretty odd to me.  I think we can just talk about tasks in the sense of ratchet, alpaca, and chain.  Anything with static (programmer-written or compiler inserted) boundaries applies}
Intermittent execution models combatting WAR can be classified into: \emph{sequential execution model} (which historically formed a baseline for this stream of research) and \emph{modular execution model} (a potent alternative, on which we base the design decisions of \sys).
)

>>>>

\subsection{Task-based Intermittent Computing}
\label{section:background_task_computing}

%\TODO{This sequential/modular split seems pretty odd to me. I think we can just talk about tasks in the sense of ratchet, alpaca, and chain.  Anything with static (programmer-written or compiler inserted) boundaries applies}

Intermittent execution models combatting WAR can be classified into: \emph{sequential execution model} (which historically formed a baseline for this stream of research) and \emph{modular execution model} (a potent alternative, on which we base the design decisions of \sys). \todo{Remove division per sequential/modular split}{Przemek}
